Eco-evolutionary dynamics of finite populations from first principles

### 2023-02-09 ind_files/06_unification_discussion.tex
Add underbraces to stochastic price

d\overline{f} &= \textrm{Cov}(w,f)dt - \frac{1}{KN_K(t)}\textrm{Cov}(\tau,f)dt\\
&+ \mu\left(1-\frac{1}{KN_K(t)}\right)\left(\sum\limits_{i=1}^{m}f_iQ_i(\mathbf{p}) - \overline{f}\sum\limits_{i=1}^{m}Q_i(\mathbf{p})\right)dt\\
&+ \frac{1}{\sqrt{K}N_{K}(t)}\left(\sum\limits_{i=1}^{m}f_i\sqrt{A_i^+}dB_{t}^{(i)} - \overline{f}\sum\limits_{i=1}^{m}\sqrt{A_i^+}dB_{t}^{(i)}\right)

>>>>

%The \vphantom is to vertically align the texts under the \underbraces
d\overline{f} &= {\underbrace{\vphantom{ \frac{1}{KN_K(t)} }\textrm{Cov}(w,f)dt}_{\substack{\text{Classical} \\ \text{selection}}}} \ \ - \ \ {\underbrace{\frac{1}{KN_K(t)}\textrm{Cov}(\tau,f)dt}_{\substack{\text{Noise-induced} \\ \text{selection}}}}\\[15pt]
&+ \underbrace{\mu\left(1-\frac{1}{KN_K(t)}\right)\left(\sum\limits_{i=1}^{m}f_iQ_i(\mathbf{p}) - \overline{f}\sum\limits_{i=1}^{m}Q_i(\mathbf{p})\right)dt}_{\text{Transmission bias/mutational effects}}\\[15pt]
&+ \underbrace{\frac{1}{\sqrt{K}N_{K}(t)}\left(\sum\limits_{i=1}^{m}f_i\sqrt{A_i^+}dB_{t}^{(i)} - \overline{f}\sum\limits_{i=1}^{m}\sqrt{A_i^+}dB_{t}^{(i)}\right)}_{\text{Stochastic fluctuations}}
